---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# onlineMessageboardActivity

<!-- badges: start -->
<!-- badges: end -->
  
The goal of onlineMessageboardActivity is to distribute the data and algorithms presented in "Modelling online discussion under circadian rhythms and superspreading dynamics" by Joe Meagher and Nial Friel.

## Installation

You can install the development version of onlineMessageboardActivity from [GitHub](https://github.com/) with:
  
 ``` r
# install.packages("devtools")
devtools::install_github("jpmeagher/onlineMessageboardActivity")
```

```{r}
library(onlineMessageboardActivity)
library(dplyr)
library(rstan)
## Stan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

## Data Examples

Data used in the manuscript is called as follows:
  
```{r data_example}
head(messageboard_df)
head(train_df)
head(test_df)
```

## Algorithm examples

Fit a model as follows

```{r fit_model}
## Prepare data
train_df <- train_df %>% 
  arrange(discussion) %>% 
  group_by(discussion) %>% 
  mutate(
    within_discussion_parent_id = refactor_branching_structure(
      id = id, parent_id = parent_id, is_immigrant = parent_id == 0, S = length(id)
    )
  ) %>% 
  mutate(within_discussion_id = seq_along(id)) %>% 
  ungroup()
a <- 48
# Specify Hyper-parameters
period <- 24 # 24 hour period
K <- 2
omega <- structure(2 * pi * (1:K / period), dim = K)
## Fit a model
fit <- fit_branching_point_process(
  t = train_df$t, branching_structure = train_df$within_discussion_parent_id,
  observation_interval = a,
  seed = 101
)
# see ?fit_branching_point_process for options
print(fit)
```

See the supplementary information accompanying the manuscript for more detail
